A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-07-11 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
NonAdditiveProbability: reworded Husimi Q example

For example, the Husimi Q functions of pure states $Q_\psi(\alpha) = \frac{1}{\pi} |\langle \alpha | \psi \rangle|^2$ have support everywhere, since we can express the inner product as \cite[eq. 11.7-1]{mandel1995}
\begin{equation}
	\langle \alpha | \psi \rangle = e^{-|\alpha|^2/2} F_\psi(\alpha^\ast)
\end{equation}
where $F_\psi$ is an entire analytic function. Conversely, in a SIC-POVM we take $d^2$ pure states $P_i$ in a $d$ dimensional space, which means they cannot be all orthogonal to each other. For a Bloch sphere, the four corners of the tetrahedron are not all opposite to each other. Therefore, disjoint sets of $P_i$ do not correspond to mutually exclusive events.

>>>>

For example, given a pure state $|\psi\>$, the Husimi Q function representing it is given by $Q_\psi(\alpha) = \frac{1}{\pi} |\langle \alpha | \psi \rangle|^2$. The inner product is given by \cite[eq. 11.7-1]{mandel1995}
\begin{equation}
	\langle \alpha | \psi \rangle = e^{-|\alpha|^2/2} F_\psi(\alpha^\ast)
\end{equation}
where $F_\psi$ is an entire analytic function, which cannot vanish on an open set without vanishing everywhere, therefore the support of all Husimi Q functions is the whole space $Z$. This means that orthogonal states, which correspond to mutually exclusive events in quantum theory, always have the same support; moreover disjoint subsets of $Z$ cannot be thought of as mutually exclusive events because event limited to any proper subset exists. For the discrete case, a SIC-POVM representation picks $d^2$ pure states $P_i$ in a $d$ dimensional space, which means they cannot be all orthogonal to each other. For a Bloch sphere, the four corners of the tetrahedron are not all opposite to each other. Therefore, disjoint sets of $P_i$ do not correspond to mutually exclusive events. Pseudo-probability representation, then, fail to be true probabilities not because of negative values, but because the points of the space do not represent mutually exclusive events.
